---
title: "Understanding the problem"
format: 
  revealjs:
    smaller: true
    scrollable: true
editor: visual
---

## Blåbærkrisa

:::: {.columns}

::: {.column width="30%"}
Same data gave different indicator values
::: 

::: {.column width="70%"}
```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example1.R")
example1
```

::: aside
Indicators with grey background
:::
:::

::::

## This project

-   250 000 kr

-   166 hours

-   1 month

-   Manuscript on pre-print server

-   Produce guidelines

---

Example with two indicators.
Scaling indicators at the sub-regions also makes it possible to
calculate an index for the sub-regions. 
But to get an index for the whole region, should we aggregate the 

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example2.R")
example2
```

---

Example of indeces at EA scale aggregated to EAA scale

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example3.R")
example3
```

---

Example of indicators aggregated at EEA scale, then turned into an index

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example4.R")
example4
```
---

However, this result is area sensitive

```{r}
#| fig-align: "left"
#| fig-height: 6
#| fig-width: 7
source("../R/example5.R")
example5
```

---
Next, variables aggregated at EAA scale